Setup

### 2019-09-26 analysis/setup.Rmd
Improved installation instructions for rticles

* `rticles`: from [`rstudio`](https://github.com/rstudio/rticles) if
  [PR #207](https://github.com/rstudio/rticles/pull/207) has been merged,
  otherwise from [`espinielli`'s branch](https://github.com/espinielli/rticles/tree/add-support-keywords)

@@

  * References on second or more line not correctly indented. (maybe re-try BibLaTeX)

>>>>

* `rticles`: from [`rstudio`](https://github.com/rstudio/rticles) if
  [PR #247](https://github.com/rstudio/rticles/pull/247) has been merged
  ```{r, eval=FALSE}
  install.packages("rticles")
  ```
  otherwise directly from [PR #247](https://github.com/rstudio/rticles/pull/247)
  ```{r, eval=FALSE}
  remotes::install_github("rstudio/rticles#247")
  ```

@@

  * References on second and subsequent lines not correctly indented.
